---
title: "Getting and Cleaning Data - Project Codebook"
author: "Anang Hudaya"
date: "Tuesday, January 20, 2015"
output: html_document
---

This codebook was generated using `knitr` tool in RStudio. It describes the variables and other relevant information inside `run_analysis.R`.



## 1. Data Source

* The data for this project has been collected from the accelerometers from the Samsung Galaxy S smartphone. A description on this dataset can be found using the following URL:
http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones
* The data for the project:
https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip
* The raw data contains in both train and test set:
  
     Type      | Training Data  | Test Data
-------------- | -------------- | -------------
Subject        | `subject_train.txt`  | `subject_test.txt`
Activity Data  | `y_train.txt`  | `y_test.txt`
Actual Data    | `x_train.txt`  | `x_test.txt`

## 2. Variable List

Here is the list of variables and their descriptions:
```{r, echo=FALSE}
desc <- c("Identifier of subject who performed the activity for each window sample. The value ranges from 1 to 30", "Activity performed by the subject", "Feature: Time or frequency signal domain", "Feature: Acceleration signal (body or gravity", "Feature: Measuring instrument used (Accelerometer or Gyroscope", "Feature: Jerk signal", "Feature: Magnitude of the signals calculated using the Euclidean norm", "Feature: Variable (Mean or Standard Deviation)", "Feature: 3-axial signals (X, Y, or Z direction)", "Feature: Count of datapoints used to compute the average", "Feature: Average reading for each activity and each subject")
columnName <- data.frame(Variable=colnames(dtTidy), description=desc)
knitr::kable(columnName)
```



## 3. Dataset Structure

Output of this program is a tidy dataset that consists of 11 variables mentioned in the previous section.

### 3.1 Summary

Below is the summary of the tidy dataset generated using `run_analysis.R`.

```{r, echo=FALSE}
summary(dtTidy)

```

### 3.2 Snapshot

A snapshot of the tidy dataset is shown below:

```{r, echo=FALSE}
head(dtTidy)
```

### 3.3 Key Variables
```{r, echo=FALSE}
key(dtTidy)
```
